---
title: "Final Project: Identification of potential buyers for eCommerce"
author: "Chen, Ruoying | Wang, Huan | Franke, Max"
output: html_notebook
---
Course: CIS-543 Programming for Big Data
Term: Fall/T2

Last modified date: 12/08/2019

Dataset avalaible:
https://archive.ics.uci.edu/ml/datasets/Online+Shoppers+Purchasing+Intention+Dataset#

# Identification of potential buyers for eCommerce  {.tabset .tabset-fade .tabset-pills}
## Workspace preparation
### Approach
***
In this section the workspace will be prepared. This means that first the global environment will be cleaned, and all 
required packages will be loaded. The data is hosted in a database in the aws Cloud and is loaded into R via a SQL 
connection. The data is transformed into R accordingly (ELT).

***
### Clean Workspace
```{r}
rm(list = ls())
```

### Install libraries
```{r}
#install.packages("tidyverse")
#install.packages("lubridate")
#install.packages("rockchalk")
#install.packages("corrplot")
#install.packages("ggcorrplot")
#install.packages("e1071")
#install.packages("ROCR")
#install.packages("rpart")
#install.packages("rpart.plot")
#install.packages("caTools")
#install.packages("party")
#install.packages("knitr")
#install.packages("rmarkdown")
#install.packages("forecast")
#install.packages("RMySQL")
#install.packages("DBI")
#install.packages("dplyr")
```

### Load Packages
```{r}
library(tidyverse)
library(lubridate)
library(rockchalk)
library(zoo)
library(corrplot)
library(e1071)
library(ROCR)
library(rpart)
library(rpart.plot)
library(caTools)
library(party)
library(knitr)
library(rmarkdown)
library(forecast)
library(RMySQL)
library(DBI)
library(dplyr)
```
### Establish Connection
```{r}
mySQLConnection <- dbConnect(MySQL(),
                             user = "bigdata",
                             password = "password",
                             dbname = "bigdata",
                             host = "bigdata.cxeixakp0jsm.us-east-1.rds.amazonaws.com",
                             port = 3306)
```
### Query Data
```{r}
# Send the query
shopper_sessions <- dbSendQuery(mySQLConnection, "SELECT * FROM shopper_sessions")

# fetch() converts the query results (stored on the server) to a local data frame
shopper_sessions <- fetch(shopper_sessions, n = -1)
```
### Head of dataset
```{r}
head(shopper_sessions)
```

### Transforming data types
```{r}
shopper_sessions$Administrative <- as.numeric(shopper_sessions$Administrative)
shopper_sessions$Administrative_Duration <- as.numeric(shopper_sessions$Administrative_Duration)
shopper_sessions$Informational <- as.numeric(shopper_sessions$Informational)
shopper_sessions$Informational_Duration <- as.numeric(shopper_sessions$Informational_Duration)
shopper_sessions$ProductRelated <- as.numeric(shopper_sessions$ProductRelated)
shopper_sessions$ProductRelated_Duration <- as.numeric(shopper_sessions$ProductRelated_Duration)
shopper_sessions$BounceRates <- as.numeric(shopper_sessions$BounceRates)
shopper_sessions$ExitRates <- as.numeric(shopper_sessions$ExitRates)
shopper_sessions$PageValues <- as.numeric(shopper_sessions$PageValues)
shopper_sessions$SpecialDay <- as.numeric(shopper_sessions$SpecialDay)
shopper_sessions$Month <- as.yearmon(shopper_sessions$Month, "%b")
shopper_sessions$Month <- month(shopper_sessions$Month, label = TRUE)
shopper_sessions$Weekend[shopper_sessions$Weekend == FALSE] <- "No"
shopper_sessions$Weekend[shopper_sessions$Weekend == TRUE] <- "Yes"
shopper_sessions$Revenue[shopper_sessions$Revenue == FALSE] <- "No"
shopper_sessions$Revenue[shopper_sessions$Revenue == TRUE] <- "Yes"
shopper_sessions$RevenueNum <- if_else(shopper_sessions$Revenue == "No", 0, 1)
shopper_sessions$ID <- c(1:length(shopper_sessions$Administrative))
```
## Data Understanding (EDA)
### Approach
***
In this section the data are examined in more detail (exploratory data analysis). The focus is on the target variable 
"Revenue". Thus, the relations of the different variables in connection with the characteristics Revenue = yes and Revenue = 
no are examined. Finally, the correlations are presented.

***

### Numerical variables
```{r}
shopper_sessions_numerical <- select(shopper_sessions, Administrative, Administrative_Duration, Informational, Informational_Duration, ProductRelated, ProductRelated_Duration, BounceRates, ExitRates, PageValues, SpecialDay)
shopper_sessions_numerical
```

### Range numerical variables
```{r}
range <- sapply(shopper_sessions_numerical, range)
range <- as.data.frame(range)
range
```
### Mean numerical variables
```{r}
mean <- sapply(shopper_sessions_numerical, mean)
mean <- as.data.frame(mean)
mean
```
### Standard deviation numerical variables
```{r}
sd <- sapply(shopper_sessions_numerical, sd)
sd <- as.data.frame(sd)
sd
```
### Bind mean and sd
```{r}
mean_sd <- cbind(mean, sd)
mean_sd
```

### Revenue per month
```{r}
# Calculate Revenue per month
Revenue_Month <- shopper_sessions %>% 
  select(Month, Revenue, ID) %>% 
  group_by(Month, Revenue) %>% 
  summarise(RevenueMonth = sum(ID))
# Plot mean revenue per month
plot1 <- ggplot(Revenue_Month, aes(x = Month, y = RevenueMonth)) + 
  geom_col(aes(fill = Revenue), width = 0.7) +
  labs(title = "Revenue per month",
       x = "Month",
       y = "Quantity revenue")
print(plot1)
```
### Revenue per VisitorType
```{r}
# Calculate Revenue per VisitorType
Revenue_VisitorType <- shopper_sessions %>% 
  select(VisitorType, Revenue, ID) %>% 
  group_by(VisitorType, Revenue) %>% 
  summarise(RevenueVisitorType = sum(ID))
Revenue_VisitorType <- Revenue_VisitorType[-c(3,4),]
# Plot mean revenue per month
plot2 <- ggplot(Revenue_VisitorType, aes(x = VisitorType, y = RevenueVisitorType)) + 
  geom_col(aes(fill = Revenue), width = 0.7) +
  labs(title = "Revenue per VisitorType",
       x = "VisitorType",
       y = "Quantity revenue")
print(plot2)
```
### Revenue per Weekend
```{r}
# Calculate Revenue per Weekend
Revenue_Weekend <- shopper_sessions %>% 
  select(Weekend, Revenue, ID) %>% 
  group_by(Weekend, Revenue) %>% 
  summarise(RevenueWeekend = sum(ID))
# Plot mean revenue per month
plot3 <- ggplot(Revenue_Weekend, aes(x = Weekend, y = RevenueWeekend)) + 
  geom_col(aes(fill = Revenue), width = 0.7) +
  labs(title = "Revenue per Weekend",
       x = "Weekend",
       y = "Quantity revenue")
print(plot3)
```
### Percentage of target variable Revenue
```{r}
# Calculate percentage of target variable Revenue
tbl_target <- table(shopper_sessions$RevenueNum)
tbl_target <- prop.table(tbl_target)
tbl_target <- as.data.frame(tbl_target)
names(tbl_target)[1] <- "Revenue"
tbl_target$RevenueString <- if_else(tbl_target$Revenue == "0", "No", "Yes")
# Plot Revenue percentage
plot4 <- ggplot(tbl_target, aes(x = RevenueString, y = Freq)) + 
  geom_bar(stat="identity", width=.5, position = "dodge") +
  geom_text(aes(label = round(Freq, 4)), position = position_stack(vjust = 0.5), col = "white") +
  labs(title = "Percentage of target variable Revenue",
       x = "Revenue",
       y = "Percentage")
print(plot4)
```
### Product Related and Product Related Duration
```{r}
# Product Related and Product Related Duration
plot5 <- ggplot(data = shopper_sessions, mapping = aes(x = ProductRelated, y = ProductRelated_Duration, col = Revenue)) +
  geom_point() +
  geom_smooth(se = F, method = "lm") +
  labs(title = "Product Related vs. Time Duration")
  #xlim(0, 400) +
  #ylim(0, 20000)
print(plot5)
```
### Bounce Rate vs Revenue
```{r}
# Calculate Bounce Rate vs Revenue
Revenue_BounceRates <- shopper_sessions %>% 
  select(BounceRates, Revenue) %>% 
  group_by(Revenue) %>% 
  summarise(RevenueBounceRates = mean(BounceRates))
# Plot
plot6 <- ggplot(data = Revenue_BounceRates, mapping = aes(x = Revenue, y = RevenueBounceRates)) +
  geom_bar(stat="identity", width=.5, position = "dodge") +
  geom_text(aes(label = round(RevenueBounceRates, 4)), position = position_stack(vjust = 0.5), col = "white") +
  labs(title = "Average Bounce Rate vs Revenue",
       y = "Average Bounce Rates")
print(plot6)
```
### Exit Rates vs Revenue
```{r}
# Calculate Exit Rates vs Revenue
Revenue_ExitRates <- shopper_sessions %>% 
  select(ExitRates, Revenue) %>% 
  group_by(Revenue) %>% 
  summarise(RevenueExitRates = mean(ExitRates))
# Plot
plot7 <- ggplot(data = Revenue_ExitRates, mapping = aes(x = Revenue, y = RevenueExitRates)) +
  geom_bar(stat="identity", width=.5, position = "dodge") +
  geom_text(aes(label = round(RevenueExitRates, 4)), position = position_stack(vjust = 0.5), col = "white") +
  labs(title = "Average Exit Rates vs Revenue",
       y = "Average Exit Rates")
print(plot7)
```
### Page Value vs Revenue
```{r}
# Calculate Page Value vs Revenue
Revenue_PageValues <- shopper_sessions %>% 
  select(PageValues, Revenue) %>% 
  group_by(Revenue) %>% 
  summarise(RevenuePageValues = mean(PageValues))
# Plot
plot8 <- ggplot(data = Revenue_PageValues, mapping = aes(x = Revenue, y = RevenuePageValues)) +
  geom_bar(stat="identity", width=.5, position = "dodge") +
  geom_text(aes(label = round(RevenuePageValues, 4)), position = position_stack(vjust = 0.5), col = "white") +
  labs(title = "Average Page Value vs Revenue",
       y = "Average Page Value")
print(plot8)
```
### Special Day vs Revenue
```{r}
# Calculate Special Day vs Revenue
Revenue_SpecialDay <- shopper_sessions %>% 
  select(SpecialDay, Revenue) %>% 
  group_by(Revenue) %>% 
  summarise(RevenueSpecialDay = mean(SpecialDay))
# Plot
plot9 <- ggplot(data = Revenue_SpecialDay, mapping = aes(x = Revenue, y = RevenueSpecialDay)) +
  geom_bar(stat="identity", width=.5, position = "dodge") +
  geom_text(aes(label = round(RevenueSpecialDay, 4)), position = position_stack(vjust = 0.5), col = "white") +
  labs(title = "Average Special Day vs Revenue",
       y = "Average Special Day")
print(plot9)
```
### Correlation for metric variables
```{r}
# Correlation
cor <- cor(shopper_sessions_numerical,
           use = "pairwise")
print(cor)
# Corrplot
corrplot <- corrplot(cor, method = "square")
print(corrplot)
```

### Summary
***
Analysis concerning the target variable Revenue shows that there are big differences between Revenue = Yes and Revenue = No 
inspected by e.g. PageValues or Special day. If these differences are significant will be analyzed  in the next section 
Hypothesis Testing.

***

## Hypothesis Testing
### Approach
***
In this section different hypotheses regarding Revenue are examined. In preparation, all box plots of numerical variables, 
divided by revenue (yes, no), are presented. For the most part, the observations from the exploratory data analysis are 
confirmed. Thus, the mean value of Page Values in the case of Revenue = yes is significant greater.

***

### Boxplot of numerical variables vs Revenue
```{r}
# Preparation
shopper_sessions_numerical$Revenue <- shopper_sessions$Revenue
namesNumerical <- names(shopper_sessions_numerical)

# for every numerical var. print boxplot vs Revenue
for (i in namesNumerical) {
  if(i != "Revenue"){
    print(ggplot(data = shopper_sessions_numerical, aes_string(x = "Revenue", y = i)) +
            geom_point(aes(colour = Revenue), alpha = 0.2, position = "jitter") +
            geom_boxplot(outlier.size=2, alpha=0.1) +
            guides(colour = FALSE) +
            labs(title = paste0("Revenue vs. ", i)))
  }
}
```
***
### Testing for numerical variables vs Revenue
#### Adminstrative: H0: mu1=mu2 [assuming normality]
```{r}
wilcox.test(formula = Administrative ~ Revenue, data = shopper_sessions, paired = FALSE, alternative = "less")
```
Reject H0, there is sufficient evidence to warrant rejection of the claim that the means are equal --> H1: Mean Yes for Administrative is greater (muY>muN)

#### Administrative_Duration: H0: mu1=mu2 [assuming normality]
```{r}
wilcox.test(formula = Administrative_Duration ~ Revenue, data = shopper_sessions, paired = FALSE, alternative = "less")
```
Reject H0, there is sufficient evidence to warrant rejection of the claim that the means are equal --> H1: Mean Yes for Administrative_Duration is greater (muY>muN)

#### Informational: H0: mu1=mu2 [assuming normality]
```{r}
wilcox.test(formula = Informational ~ Revenue, data = shopper_sessions, paired = FALSE, alternative = "less")
```
Reject H0, there is sufficient evidence to warrant rejection of the claim that the means are equal --> H1: Mean Yes for Informational is greater (muY>muN)

#### Informational_Duration: H0: mu1=mu2 [assuming normality]
```{r}
wilcox.test(formula = Informational_Duration ~ Revenue, data = shopper_sessions, paired = FALSE, alternative = "less")
```
Reject H0, there is sufficient evidence to warrant rejection of the claim that the means are equal --> H1: Mean Yes for Informational_Duration is greater (muY>muN)

#### ProductRelated: H0: mu1=mu2 [assuming normality]
```{r}
wilcox.test(formula = ProductRelated ~ Revenue, data = shopper_sessions, paired = FALSE, alternative = "less")
```
Reject H0, there is sufficient evidence to warrant rejection of the claim that the means are equal --> H1: Mean Yes for ProductRelated is greater (muY>muN)

#### ProductRelated_Duration: H0: mu1=mu2 [assuming normality]
```{r}
wilcox.test(formula = ProductRelated_Duration ~ Revenue, data = shopper_sessions, paired = FALSE, alternative = "less")
```
Reject H0, there is sufficient evidence to warrant rejection of the claim that the means are equal --> H1: Mean Yes for ProductRelated_Duration is greater (muY>muN)

#### Bounce Rates: H0: mu1=mu2 [assuming normality]
```{r}
wilcox.test(formula = BounceRates ~ Revenue, data = shopper_sessions, paired = FALSE, alternative = "greater")
```
Reject H0, there is sufficient evidence to warrant rejection of the claim that the means are equal --> H1: Mean No for Bounce Rate is greater (muN>muY)

#### Exit Rates: H0: mu1=mu2 [assuming normality]
```{r}
wilcox.test(formula = ExitRates ~ Revenue, data = shopper_sessions, paired = FALSE, alternative = "greater")
```
Reject H0, there is sufficient evidence to warrant rejection of the claim that the means are equal --> H1: Mean No for Exit Rates is greater (muN>muY)

#### Page Value: H0: mu1=mu2 [assuming normality]
```{r}
wilcox.test(formula = PageValues ~ Revenue, data = shopper_sessions, paired = FALSE, alternative = "less")
```
Reject H0, there is sufficient evidence to warrant rejection of the claim that the means are equal --> H1: Mean Yes for Page Values is greater (muY>muN)

#### Special Day: H0: mu1=mu2 [assuming normality]
```{r}
wilcox.test(formula = SpecialDay ~ Revenue, data = shopper_sessions, paired = FALSE, alternative = "greater")
```
Reject H0, there is sufficient evidence to warrant rejection of the claim that the means are equal --> H1: Mean No for Page Values is greater (muN>muY)

### Summary
***
It is statistically proved that significant differences between Revenue = yes and Revenue = no regarding variables in the 
data set, such as bounce rates:
It is demonstrated that if Revenue = no, the Bounce Rates are greater in comparison Revenue = yes. This approach in 
conclusion can be transferred to all Hypothesis tests.

***

## Model Building & Prediction
### Approach
***
In this section the models to answer the main problem are built and predicted. First the workspace is cleaned again and the 
dataset is imported in raw version (connection to Cloud Database). In addition, the data is then transformed. 
The findings from the previous analyses are implemented. Thus rare instances of selected categorical variables are combined, 
e.g. Operating System with the characteristics 5,6,7,8 to "Other". 
In preparation for the models, the data set is divided with the ratio 3:1 into training and test data with a random seed. The 
models are trained with the training data and later evaluated with the test data.
The following models are built to identify potential buyers:
1. Logistic Regression Model
2. Decision Tree (rpart)
3. decision tree (ctree)
4. Naive Bayes
Finally, the models are predicted in conjunction with the test data set.

***

### Datasets as start and summarize rare instances of selected categorical variables
#### Clean workspace
```{r}
rm(list = ls())
```
#### Establish Connection
```{r}
mySQLConnection <- dbConnect(MySQL(),
                             user = "bigdata",
                             password = "password",
                             dbname = "bigdata",
                             host = "bigdata.cxeixakp0jsm.us-east-1.rds.amazonaws.com",
                             port = 3306)
```
#### Query Data
```{r}
# Send the query
shopper_sessions <- dbSendQuery(mySQLConnection, "SELECT * FROM shopper_sessions")

# fetch() converts the query results (stored on the server) to a local data frame
shopper_sessions <- fetch(shopper_sessions, n = -1)
```
#### Transforming data types
```{r}
shopper_sessions$Administrative <- as.numeric(shopper_sessions$Administrative)
shopper_sessions$Administrative_Duration <- as.numeric(shopper_sessions$Administrative_Duration)
shopper_sessions$Informational <- as.numeric(shopper_sessions$Informational)
shopper_sessions$Informational_Duration <- as.numeric(shopper_sessions$Informational_Duration)
shopper_sessions$ProductRelated <- as.numeric(shopper_sessions$ProductRelated)
shopper_sessions$ProductRelated_Duration <- as.numeric(shopper_sessions$ProductRelated_Duration)
shopper_sessions$BounceRates <- as.numeric(shopper_sessions$BounceRates)
shopper_sessions$ExitRates <- as.numeric(shopper_sessions$ExitRates)
shopper_sessions$PageValues <- as.numeric(shopper_sessions$PageValues)
shopper_sessions$SpecialDay <- as.numeric(shopper_sessions$SpecialDay)
shopper_sessions$Month <- as.yearmon(shopper_sessions$Month, "%b")
shopper_sessions$Month <- month(shopper_sessions$Month, label = TRUE)
shopper_sessions$Weekend[shopper_sessions$Weekend == FALSE] <- "No"
shopper_sessions$Weekend[shopper_sessions$Weekend == TRUE] <- "Yes"
shopper_sessions$VisitorType <- as.factor(shopper_sessions$VisitorType)
shopper_sessions$Weekend <- as.factor(shopper_sessions$Weekend)
shopper_sessions$Revenue[shopper_sessions$Revenue == FALSE] <- "No"
shopper_sessions$Revenue[shopper_sessions$Revenue == TRUE] <- "Yes"
shopper_sessions$Revenue <- as.factor(shopper_sessions$Revenue)
# Summarize rare instances of selected categorical variables
# 5 to 8 of Operating Systems
shopper_sessions$OperatingSystems <-  as.factor(shopper_sessions$OperatingSystems)
shopper_sessions$OperatingSystems <- combineLevels(shopper_sessions$OperatingSystems, levs = c("5","6", "7", "8"), newLabel = "Other")
# Browser: 8, 9, 11, 12, 13, 7 & 3
shopper_sessions$Browser <- as.factor(shopper_sessions$Browser)
shopper_sessions$Browser <- combineLevels(shopper_sessions$Browser, levs = c("8","9", "11", "12", "13", "7", "3"), newLabel = "Other")
# Traffic Type: 7, 9, 12, 14, 15, 16, 17, 18
shopper_sessions$TrafficType <- as.factor(shopper_sessions$TrafficType)
shopper_sessions$TrafficType <- combineLevels(shopper_sessions$TrafficType, levs = c("7","9", "12", "14", "15", "16", "17", "18"), newLabel = "Other")
head(shopper_sessions)
```
### Create training and test data
```{r}
require(caTools)

# Set the random seed for repeatability
set.seed(123)

# Split the data into Ratio 3:1
sample <- sample.split(shopper_sessions$Revenue, SplitRatio = .75)
train <- subset(shopper_sessions, sample == TRUE)
test <- subset(shopper_sessions, sample == FALSE)

# Data sets with all independent variables for training the dependent variable "Revenue"
train_x <- train[,-which(names(train) %in% "Revenue")]
train_y <- factor(train$Revenue)

# Data sets with all independent variables for test the dependent variable "Revenue"
test_x <- test[,-which(names(test) %in% "Revenue")]
test_y <- factor(test$Revenue)
```
***
### Logistic Regression Model
```{r}
# Preparation
train_num <- select(train, Administrative, Administrative_Duration, Informational, Informational_Duration, ProductRelated, ProductRelated_Duration, BounceRates, ExitRates, PageValues, SpecialDay, Revenue)
test_num <- select(test, Administrative, Administrative_Duration, Informational, Informational_Duration, ProductRelated, ProductRelated_Duration, BounceRates, ExitRates, PageValues, SpecialDay, Revenue)

# Build model
glm_model <- glm(formula = Revenue ~., data = train_num, family = binomial(link = "logit"))
summary(glm_model)

# Create glm model 2, just with sig values from glm model
glm_model2 <- glm(formula = Revenue ~ ProductRelated + ExitRates + PageValues + SpecialDay, data = train_num, family = binomial(link = "logit"))
summary(glm_model2)

```
***
### Decision Tree (rpart)
#### Build model
```{r}
dt_model <- rpart(formula =  Revenue ~., data = train, 
                  method = "class", control = rpart.control(cp = 0.0001))
printcp(dt_model)
```
#### Visualize complexity parameters
```{r}
plotcp(dt_model)
```
#### Optimize complexity parameters
```{r}
dt_model <- rpart(formula =  Revenue ~ ., data = train, 
                  method = "class", control = rpart.control(cp = 0.001))
# Print model
printcp(dt_model)
```
#### Visualize Decision Tree
```{r}
rpart.plot(dt_model, main = "Decision Tree")
```
#### Importance of variables
```{r}
importance.dt <- dt_model$variable.importance
barplot(dt_model$variable.importance, main ="Importance of variables",horiz = TRUE, las = 1, cex.names = 0.5)
```
***
### Decision Tree (ctree)
```{r}
dt_model2 <- ctree(Revenue ~ ., data = train)
```
#### Plot the tree
```{r}
plot(dt_model2)
```

***

### Naive Bayes
```{r}
nb_model <- naiveBayes(Revenue ~ ., data = train, laplace = 20)
nb_model
```
***
### Prediction
```{r}
pred_test_glm <- predict(glm_model2, test_num, type = "response")
pred_test_dt <- predict(dt_model, newdata = test, type = "class")
pred_test_dt2 <- predict(dt_model2, test)
pred_test_nb <- predict(nb_model, newdata = test, type = "class")
```

### Summary
***
logistic regression model is rebuilt with only significantly important variables. The formula of new logistic model is:
Revenue = -1.980645 + 0.005385 * Product Related -  19.603015 * Exit Rate + 0.081696 Page Value – 0.867538 Special Day

The rpart tree model is first built with complexity parameter equaling 0.0001, and then the model is optimized with 
complexity parameter equaling 0.001. 

The ctree tree model is built. First cut is PageValues and then Month and PageValues.

In naive bayes model, laplace is 20 to reduce the effect of unavailable records in the train set.

***


## Performance Measurement
### Approach
***
In this section the models are evaluated according two criteria Accuracy & AUC values, whereby the decision for the best 
model is made on the basis of Accuracy.
In order to calculate the accuracy, the confusion matrixes are first established, whereby the predictions still have to be 
transformed with regard to the "logistic regression" model into "yes" and "no". Using the elements of the confusion matrix 
(TP,TN,FP,FN) and the other results (Actual and Prediction data frame), the accuracy is calculated and presented. Finally, it 
is examined whether there is a significant difference between the models with regard to accuracy. 
The package ROCR is used to calculate the AUC values and ROC curves. Therefore, a prediction obejct is first created that 
brings the input data into a standardized form. Then ROC and AUC are determined and plotted with the ROC curves of all models 
with corresponding AUC values. Finally, the extent to which the training vs. test ROC and AUC values differ is examined with 
regard to overfitting. 

***

### Confusion matrix
```{r}
glm_confusion_matrix <- table(test_num$Revenue, pred_test_glm, dnn = c("Actual", "Prediction"))
dt_confusion_matrix <- table(test$Revenue, pred_test_dt, dnn = c("Actual", "Prediction"))
dt2_confusion_matrix <- table(test$Revenue, pred_test_dt2, dnn = c("Actual", "Prediction"))
nb_confusion_matrix <- table(test$Revenue, pred_test_nb, dnn = c("Actual", "Prediction"))

# Print [glm shows probabilities and is not useful to be displayed now]
print(dt_confusion_matrix)
print(dt2_confusion_matrix)
print(nb_confusion_matrix)
```
### Output results
```{r}
glm_results <- data.frame(Actual = test_num$Revenue,
                          Prediction = pred_test_glm)

dt_results <- data.frame(Actual = test_num$Revenue,
                          Prediction = pred_test_dt)

dt2_results <- data.frame(Actual = test_num$Revenue,
                          Prediction = pred_test_dt2)

nb_results <- data.frame(Actual = test_num$Revenue,
                          Prediction = pred_test_nb)
print(glm_results)
print(dt_results)
print(dt2_results)
print(nb_results)
```
***
### Transform Prediction for logistic regression
```{r}
glm_results$Prediction <- if_else(glm_results$Prediction > 0.5, "yes", "no")
print(glm_results)
```
***
### Accuracy calculation
#### Logisitc regression
```{r}
# Elements of confusion matrix
TP <- subset(glm_results, Actual == "Yes", Prediction == "Yes")
TN <- subset(glm_results, Actual == "No", Prediction == "No")
FN <- subset(glm_results, Actual == "Yes", Prediction == "No")
FP <- subset(glm_results, Actual == "No", Prediction == "Yes")
# Calculate Accuracy
glm_accuracy <- (nrow(TP)+nrow(TN))/ (nrow(TP)+nrow(TN)+nrow(FN)+nrow(FP))
# Output results
cat("Accuracy for log regression is: ", glm_accuracy, "\n")

# Save Accuracy for comparison
glm_TP <- if_else(glm_results$Actual == glm_results$Prediction, 1, 0)
glm_TP <- as.data.frame(glm_TP)
glm_TP$Model <- "Log regression"
names(glm_TP)[1] <- "Accuracy"
```

#### Decision tree rpart
```{r}
# Elements of confusion matrix
TP <- dt_confusion_matrix[2,2]
TN <- dt_confusion_matrix[1,1]
FN <- dt_confusion_matrix[1,2]
FP <- dt_confusion_matrix[2,1]
# Calculate Accuracy
dt_accuracy <- (TP+TN)/sum(TP, TN, FN, FP)
# Output results
cat("Accuracy for rpart is: ", dt_accuracy, "\n")

# Save Accuracy for ctree
dt_TP <- if_else(dt_results$Actual == dt_results$Prediction, 1, 0)
dt_TP <- as.data.frame(dt_TP)
dt_TP$Model <- "rpart"
names(dt_TP)[1] <- "Accuracy"
```

#### Decision tree ctree
```{r}
# Elements of confusion matrix
TP <- dt2_confusion_matrix[2,2]
TN <- dt2_confusion_matrix[1,1]
FN <- dt2_confusion_matrix[1,2]
FP <- dt2_confusion_matrix[2,1]
# Calculate Accuracy
dt2_accuracy <- (TP+TN)/sum(TP, TN, FN, FP)
# Output results
cat("Accuracy for ctree is: ", dt2_accuracy, "\n")

# Save Accuracy for ctree
dt2_TP <- if_else(dt2_results$Actual == dt2_results$Prediction, 1, 0)
dt2_TP <- as.data.frame(dt2_TP)
dt2_TP$Model <- "ctree"
names(dt2_TP)[1] <- "Accuracy"
```

#### Naive Bayes
```{r}
# Elements of confusion matrix
TP <- nb_confusion_matrix[2,2]
TN <- nb_confusion_matrix[1,1]
FN <- nb_confusion_matrix[1,2]
FP <- nb_confusion_matrix[2,1]
# Calculate Accuracy
nb_accuracy <- (TP+TN)/sum(TP, TN, FN, FP)
# Output results
cat("Accuracy for Naive Bayes is: ", nb_accuracy, "\n")

# Save Accuracy for Naive Bayes
nb_TP <- if_else(nb_results$Actual == nb_results$Prediction, 1, 0)
nb_TP <- as.data.frame(dt_TP)
nb_TP$Model <- "Naive Bayes"
names(dt_TP)[1] <- "Accuracy"
```
***
### Accuracy comparison
```{r}
compare <- data.frame(Method = c("04-Logistic Regression", "03-Naive Bayes", "01-Decision Tree rpart", "02-Decision Tree ctree"),
                      Accuracy = c(glm_accuracy, nb_accuracy, dt_accuracy, dt2_accuracy))
compare
ggplot(data = compare, mapping = aes(x = Method, y = Accuracy)) +
  geom_col() +
  geom_text(aes(label = round(Accuracy, 4)), position = position_stack(vjust = 0.5), col = "white") +
  labs(title = "Accuracy comparison between different models")
  
TruePositive <- rbind(glm_TP, dt_TP, dt2_TP, nb_TP)
TruePositive <- as.data.frame(TruePositive)
TruePositive$Model <- as.factor(TruePositive$Model)
aov <- aov(Accuracy ~ Model, data = TruePositive)
summary(aov)
TukeyHSD(aov)
```
### Print out the significant differences
```{r}
# Safe Tukey test
Tukey <- TukeyHSD(aov)
Tukey <- as.data.frame(Tukey$Model)
# Print results
cat("P-Value Log regression - ctree: ", Tukey$`p adj`[1],", reject H0 - sig. difference.", "\n")
cat("P-Value Naive Bayes - ctree: ", Tukey$`p adj`[2],", fail to reject H0, no sig. differnce.", "\n")
cat("P-Value rpart - ctree: ", Tukey$`p adj`[3],", fail to reject H0, no sig. differnce.", "\n")
cat("P-Value Naive Bayes - Log regression: ", Tukey$`p adj`[4],", reject H0 - sig. difference.", "\n")
cat("P-Value rpart - Log regression: ", Tukey$`p adj`[5],", reject H0 - sig. difference.", "\n")
cat("P-Value rpart - Naive Bayes: ", Tukey$`p adj`[6],", fail to reject H0, no sig. differnce.")
```


### Summary
***
The best fitted model is rpart decision tree. Concerning anova, there is significant difference between the models concerning 
accuracy (H0: means of the accuracy values are equal between the models) --> p-value = <2e-16 < 0.05, reject H0.
There is sufficient evidence to warrant rejection of the claim that the Accuracy from the models are equal (TukeyHSD Test: 
Logistic regression is significant different).
***

### Performance Measurement (ROCR)
### Prediction with probalities
```{r}
pred_test_glm <- predict(glm_model, test_x, type = "response")
pred_test_dt <- predict(dt_model, newdata = test, type = "prob")
pred_test_dt2 <- sapply(predict(dt_model2, newdata = test_x, type="prob"),'[[',2)
pred_test_nb <- predict(nb_model, newdata = test_x, type = "raw")
```
### Creating a prediction object (transform input data into a standardized format)
```{r}
prediction_test_dt <- prediction(pred_test_dt[,2], labels = test$Revenue)
prediction_test_dt2 <- prediction(pred_test_dt2, labels = test$Revenue)
prediction_test_nb <- prediction(pred_test_nb[,2], labels = test$Revenue)
prediction_test_glm <- prediction(pred_test_glm, labels = test$Revenue)
```
***
### ROC & AUC
#### Calculate ROC
```{r}
roc_test_dt <- performance(prediction_test_dt, measure ="tpr", x.measure ="fpr")
roc_test_dt2 <- performance(prediction_test_dt2, measure = "tpr", x.measure = "fpr")
roc_test_nb <- performance(prediction_test_nb, measure = "tpr", x.measure = "fpr")
roc_test_glm <- performance(prediction_test_glm, measure="tpr", x.measure="fpr")
```
#### Calculate AUC
```{r}
auc_test_dt <- performance(prediction_test_dt, measure = "auc")
auc_test_dt2 <- performance(prediction_test_dt2, measure = "auc")
auc_test_nb <- performance(prediction_test_nb, measure = "auc")
auc_test_glm <- performance(prediction_test_glm, measure = "auc")
```
#### Output of AUC values rounded depending on model 
```{r}
auc_test_dt <- round(auc_test_dt@y.values[[1]], 4)
auc_test_dt2 <- round(auc_test_dt2@y.values[[1]], 4)
auc_test_nb <- round(auc_test_nb@y.values[[1]], 4)
auc_test_glm <- round(auc_test_glm@y.values[[1]], 4)
```
#### Plot of all ROC curves with corresponding AUC values for visual comparison
```{r}
plot(roc_test_dt, main = "All ROC curves")
plot(roc_test_dt2, add = TRUE, col = "darkgreen")
plot(roc_test_nb, add = TRUE, col = "red")
plot(roc_test_glm, add = TRUE, col = "blue")
abline(0,1, col = "grey", lty = 2)
legend("bottomright", legend = c(paste0("Decision Tree rpart (AUC = ", auc_test_dt, ")"),
                                 paste0("Decision Tree ctree (AUC = ", auc_test_dt2, ")"),
                                 paste0("Naive Bayes (AUC = ", auc_test_nb, ")"),
                                 paste0("Logistic Regression (AUC = ", auc_test_glm, ")")),
       col = c("black","darkgreen","red","blue"), lty = c(1,1,1,1))
```
***
### Plot Test-AUC vs Train-AUC
#### Decision Tree rpart Test vs Train ROC & AUC
```{r}
# Calculate values for train
pred_train_dt <- predict(dt_model, newdata = train_x, type = "prob")
prediction_train_dt <- prediction(pred_train_dt[,2], labels = train$Revenue)
roc_train_dt <- performance(prediction_train_dt, measure="tpr", x.measure="fpr")
auc_train_dt <- performance(prediction_train_dt, measure="auc")
auc_train_dt <- round(auc_train_dt@y.values[[1]], 4)
# Plot
plot(roc_train_dt, main = "Decision Tree rpart: Train-ROC vs Test-ROC")
plot(roc_test_dt, add = TRUE, col = "red")
abline(0,1, col = "grey", lty = 2)
legend("bottomright", legend = c(paste0("Decision Tree Train (AUC = ", auc_train_dt, ")"),
                                 paste0("Decision Tree Test (AUC = ", auc_test_dt, ")")),
       col = c("black", "red"), lty = c(1,1))
```
#### Decision Tree ctree Test vs Train ROC & AUC
```{r}
# Calculate values for train
pred_train_dt2 <- sapply(predict(dt_model2, newdata = train_x, type = "prob"),'[[',2)
prediction_train_dt2 <- prediction(pred_train_dt2, labels = train$Revenue)
roc_train_dt2 <- performance(prediction_train_dt2, measure = "tpr", x.measure = "fpr")
auc_train_dt2 <- performance(prediction_train_dt2, measure = "auc")
auc_train_dt2 <- round(auc_train_dt2@y.values[[1]], 4)
# Plot
plot(roc_train_dt2, main = "Decision Tree ctree: Train-ROC vs. Test-ROC")
plot(roc_test_dt2, add = TRUE, col = "red")
abline(0,1, col = "grey", lty = 2)
legend("bottomright", legend = c(paste0("Decision Tree Train (AUC = ", auc_train_dt2, ")"),
                                 paste0("Decision Tree Test (AUC = ", auc_test_dt2, ")")),
       col = c("black", "red"), lty = c(1,1))
```
#### Naive Bayes Test vs Train ROC & AUC
```{r}
# Calculate values for train
pred_train_nb <- predict(nb_model, newdata = train_x, type = "raw")
prediction_train_nb <- prediction(pred_train_nb[,2], labels = train$Revenue)
roc_train_nb <- performance(prediction_train_nb, measure="tpr", x.measure="fpr")
auc_train_nb <- performance(prediction_train_nb, measure="auc")
auc_train_nb <- round(auc_train_nb@y.values[[1]], 4)
# Plot
plot(roc_train_nb, main = "Naive Bayes: Train-ROC vs Test-ROC")
plot(roc_test_nb, add = TRUE, col = "red")
abline(0,1, col = "grey", lty = 2)
legend("bottomright", legend = c(paste0("Naive Bayes Train (AUC = ", auc_train_nb, ")"),
                                 paste0("Naive Bayes Test (AUC = ", auc_test_nb, ")")),
       col = c("black", "red"), lty = c(1,1))
```
#### Logistic Regression vs Train ROC & AUC
```{r}
# Calculate values for train
pred_train_glm <- predict(glm_model, newdata = train_x, type = "response")
prediction_train_glm <- prediction(pred_train_glm, labels = train$Revenue)
roc_train_glm <- performance(prediction_train_glm, measure="tpr", x.measure="fpr")
auc_train_glm <- performance(prediction_train_glm, measure="auc")
auc_train_glm <- round(auc_train_glm@y.values[[1]], 4)
# Plot
plot(roc_train_glm, main = "Logistic Regression: Train-ROC vs Test-ROC")
plot(roc_test_glm, add = TRUE, col = "red")
abline(0,1, col = "grey", lty = 2)
legend("bottomright", legend = c(paste0("Logistic Regression Train (AUC = ", auc_train_glm, ")"),
                                 paste0("Logistic Regression Test (AUC = ", auc_test_glm, ")")),
       col = c("black", "red"), lty = c(1,1))
```

### Summary
***
Concerning the AUC values ctree is performaing the best. For this project the performance measuerment is focusing on 
accuracy. Regardless this, there is no big difference between Train ROC and Test ROC for all models, so there is no 
overfitting.

***

## Linear Regression
### Approach
***
In this section it is tried to explain the variable Page Values using linear regression models, because this variable has a 
high influence on Revenue. So it is interesting to know the relation of Page Values to the other variables. For this, the 
methods of backward elimination and forward selection are used. Finally, it is checked whether the quality of the model can 
be improved by a possible transformation.

***

### Correlation matrix
```{r}
shopper_sessions_numerical <- select(shopper_sessions, Administrative, Administrative_Duration, Informational, Informational_Duration, ProductRelated, ProductRelated_Duration, BounceRates, ExitRates, SpecialDay, PageValues)
pairs(shopper_sessions_numerical)
```
### Revenue can't be part of the models
```{r}
shopper_sessions <- shopper_sessions[,1:17]
```

### Complete model
```{r}
completeModel <- lm(formula = PageValues ~ ., data = shopper_sessions)
summary(completeModel)
anova <- anova(completeModel)
anova
```
### Backward elimination
```{r}
full.model <- lm(PageValues ~ ., 
                 data = shopper_sessions)
# stepwise
step(object = full.model, # start at the full model
    direction = "backward") # allow it remove predictors but not add them

# the result of the best regression model it could find:
lmBackward <- lm(PageValues ~ Administrative + ProductRelated + BounceRates + 
    ExitRates + SpecialDay + Month + OperatingSystems + TrafficType + 
    VisitorType, data = shopper_sessions)
summary(lmBackward)
anovaBackward <- anova(lmBackward)
anovaBackward
```
### Forward selection
```{r}
null.model <- lm(PageValues ~ 1, shopper_sessions)
step(object = null.model,
     direction = "forward",
     scope = PageValues ~ Administrative + Administrative_Duration + Informational + Informational_Duration + ProductRelated + ProductRelated_Duration + BounceRates + ExitRates + PageValues + SpecialDay + Month + OperatingSystems + Browser + Region + TrafficType + VisitorType + Weekend)

# the result of the best regression model it could find:
lm_forward <- lm(PageValues ~ ExitRates + BounceRates + VisitorType + 
    OperatingSystems + TrafficType + SpecialDay + Month + Administrative + 
    ProductRelated, data = shopper_sessions)
summary(lm_forward)
anovaForward <- anova(lm_forward)
anovaForward
```
### Transformation of PageValue in order to increase R2
```{r}
plot(lm_forward)
hist(lm_forward$residuals, main = "Histogram of residuals with Page Value")
lm_sqrt <- lm(formula = sqrt(PageValues) ~ ExitRates + BounceRates + VisitorType + 
    SpecialDay + Month + Browser + Administrative, data = shopper_sessions)
summary(lm_sqrt)
plot(lm_sqrt)
hist(lm_sqrt$residuals, main = "Histogram of residuals with sqrt(Page Value)")
```

### Summary
***
Both methods (forward selection, backwards elimination) show the same result, the explanation of Page Value is concerning R2 
low.
The transformation shows an increased R2 but the total R2 is still low.

***

## Clustering
### Approach
***
In this section the goal is to grouping a session's behaviour concerning Bounce Rate & Exit Rate splitted by Revenue. 
Therefore, it Revenue is splitted into "no" and "yes". For every split the kmeans algorighm is performed. To pick the right 
k, the elbow criteria is used, which can be seen in wss. The clusters and the right pick for k (elbow criteria) is 
visualized.

***

### Clean Workspace
```{r}
rm(list = ls())
```
### Establish Connection
```{r}
mySQLConnection <- dbConnect(MySQL(),
                             user = "bigdata",
                             password = "password",
                             dbname = "bigdata",
                             host = "bigdata.cxeixakp0jsm.us-east-1.rds.amazonaws.com",
                             port = 3306)
```
### Query Data
```{r}
# Send the query
shopper_sessions <- dbSendQuery(mySQLConnection, "SELECT * FROM shopper_sessions")

# fetch() converts the query results (stored on the server) to a local data frame
shopper_sessions <- fetch(shopper_sessions, n = -1)
```
### Data transformation
```{r}
shopper_sessions$Administrative <- as.numeric(shopper_sessions$Administrative)
shopper_sessions$Administrative_Duration <- as.numeric(shopper_sessions$Administrative_Duration)
shopper_sessions$Informational <- as.numeric(shopper_sessions$Informational)
shopper_sessions$Informational_Duration <- as.numeric(shopper_sessions$Informational_Duration)
shopper_sessions$ProductRelated <- as.numeric(shopper_sessions$ProductRelated)
shopper_sessions$ProductRelated_Duration <- as.numeric(shopper_sessions$ProductRelated_Duration)
shopper_sessions$BounceRates <- as.numeric(shopper_sessions$BounceRates)
shopper_sessions$ExitRates <- as.numeric(shopper_sessions$ExitRates)
shopper_sessions$PageValues <- as.numeric(shopper_sessions$PageValues)
shopper_sessions$SpecialDay <- as.numeric(shopper_sessions$SpecialDay)
shopper_sessions$Month <- as.yearmon(shopper_sessions$Month, "%b")
shopper_sessions$Month <- month(shopper_sessions$Month, label = TRUE)
shopper_sessions$Weekend[shopper_sessions$Weekend == FALSE] <- "No"
shopper_sessions$Weekend[shopper_sessions$Weekend == TRUE] <- "Yes"
shopper_sessions$Revenue[shopper_sessions$Revenue == FALSE] <- "No"
shopper_sessions$Revenue[shopper_sessions$Revenue == TRUE] <- "Yes"
shopper_sessions$RevenueNum <- if_else(shopper_sessions$Revenue == "No", 0, 1)
shopper_sessions$ID <- c(1:length(shopper_sessions$Administrative))
```
***
### Revenue = "no"
#### Plot relationship
```{r}
cluster_dataset <- subset(shopper_sessions, Revenue == "No", select = c(BounceRates, ExitRates, Revenue))

# Plot 
ggplot(data = cluster_dataset, mapping = aes(BounceRates, ExitRates, color = Revenue)) +
  geom_point() +
  labs(title = "Bounce vs. Exit Rates (Revenue = no)")
```
#### Set the random seed
```{r}
set.seed(20)
```
#### Extract only Bounce Rate and Exit Rate data for clustering
```{r}
Rate <- data.frame(length = cluster_dataset$BounceRates, width = cluster_dataset$ExitRates)
head(Rate)
```
#### Perform Algorithm
##### Perform kmeans with k set to 4
```{r}
RateCluster <- kmeans(Rate, centers =  4, nstart = 25)
print(RateCluster)
```
#### Verification and Visualization
##### Verfication
```{r}
table(RateCluster$cluster, cluster_dataset$Revenue)
```
##### Add the cluster assignment to each point
```{r}
cluster_dataset$Cluster <- as.factor(RateCluster$cluster)
```
##### Get centroids
```{r}
centroids <- as.data.frame(RateCluster$centers)
centroids$Cluster <- as.factor(c(1:4))
```
##### Visualize cluster assignments
```{r}
ggplot(data = cluster_dataset, mapping = aes(BounceRates, ExitRates, color = Cluster)) +
  geom_point() +
  geom_point(data = centroids, aes(length, width, fill = Cluster), size = 5, shape = 13) +
  labs(title = "Cluster between Exit & Bounce Rates (Revenue = no)")
```
#### Picking K
##### For each k, perform WSS, store the value
```{r}
wss <- numeric(15)
for (k in 1:15) {
  wss[k] = sum(kmeans(Rate, k, nstart = 25)$withinss)
}
```
##### Make a data frame out of the WSS results
```{r}
wssResults <- data.frame(k = c(1:15), wss = wss)
wssResults
```
##### Visualize WSS
```{r}
ggplot(data = wssResults, mapping = aes(x = k, y = wss)) +
  geom_point() +
  geom_line() + 
  labs(title = "K-means (Revenue = no)", x = "Number of Clusters k", y = "Within Sum of Squares")
```
***
### Revenue = "yes"
#### Plot relationship
```{r}
cluster_dataset <- subset(shopper_sessions, Revenue == "Yes", select = c(BounceRates, ExitRates, Revenue))

# Plot 
ggplot(data = cluster_dataset, mapping = aes(BounceRates, ExitRates, color = Revenue)) +
  geom_point() +
  geom_point() +
  labs(title = "Bounce vs. Exit Rates (Revenue = yes)")
```
#### Set the random seed
```{r}
set.seed(20)
```
#### Extract only Bounce Rate and Exit Rate data for clustering
```{r}
Rate <- data.frame(length = cluster_dataset$BounceRates, width = cluster_dataset$ExitRates)
head(Rate)
```
#### Perform Algorithm
##### Perform kmeans with k set to 3
```{r}
RateCluster <- kmeans(Rate, centers =  4, nstart = 25)
print(RateCluster)
```
#### Verification and Visualization
##### Verfication
```{r}
table(RateCluster$cluster, cluster_dataset$Revenue)
```
##### Add the cluster assignment to each point
```{r}
cluster_dataset$Cluster <- as.factor(RateCluster$cluster)
```
##### Get centroids
```{r}
centroids <- as.data.frame(RateCluster$centers)
centroids$Cluster <- as.factor(c(1:4))
```
##### Visualize cluster assignments
```{r}
ggplot(data = cluster_dataset, mapping = aes(BounceRates, ExitRates, color = Cluster)) +
  geom_point() +
  geom_point(data = centroids, aes(length, width, fill = Cluster), size = 5, shape = 13) +
  labs(title = "Cluster between Exit & Bounce Rates (Revenue = yes)")
```
#### Picking K
##### For each k, perform WSS, store the value
```{r}
wss <- numeric(15)
for (k in 1:15) {
  wss[k] = sum(kmeans(Rate, k, nstart = 25)$withinss)
}
```
##### Make a data frame out of the WSS results
```{r}
wssResults <- data.frame(k = c(1:15), wss = wss)
wssResults
```
##### Visualize WSS
```{r}
ggplot(data = wssResults, mapping = aes(x = k, y = wss)) +
  geom_point() +
  geom_line() + 
  labs(title = "K-means (Revenue = yes)", x = "Number of Clusters k", y = "Within Sum of Squares")
```

### Summary
***
The best k to pick is for both cases 4.
Clustering does not allow any grouping between bounce and exit rate in terms of revenue.

***

## Time Series Analysis
### Approach
***
In this section the variable PageValue is examined over the consecutive months. Since the number of months is small, the 
significance of this analysis will be limited.

***
### Visualize data
```{r}
# Summarise the mean PageValues per month
PageValue_Month <- shopper_sessions %>%
  select(c(PageValues, Month)) %>%
  filter(Month > "Mar") %>%
  group_by(Month) %>%
  summarise(PageValues = mean(PageValues))
PageValue_Month
# Plot
ggplot(data = PageValue_Month, mapping = aes(x = Month, y = PageValues)) +
  geom_col() +
  geom_text(aes(label = round(PageValues, 4)), position = position_stack(vjust = 0.5), col = "white") +
  labs(title = "Average PageValues per Month")
  
```

### Dataset
```{r}
time_series <- subset(shopper_sessions, Month > "Mar", select = c(Month, PageValues))
time_series$Month <- as.yearmon(time_series$Month, "%b")
time_series$Month <- month(time_series$Month, label = T)
head(time_series)
```
### Create time-series object
```{r}
shopper_sessions_TS <- ts(time_series$PageValues, start = 5, end = 12, frequency = 8)
shopper_sessions_TS
```
### Decompose the time series
```{r}
Month_pagevalueDecomposition <- decompose(shopper_sessions_TS)
```
### Plot the decomposition
```{r}
plot(Month_pagevalueDecomposition)
```
### Create Training and Testing Sets
```{r}
# training set: May to 1956
train = window(shopper_sessions_TS, start = 5, end = 10)

# test set:  1957 to 1960 
test = window(shopper_sessions_TS, start = 11, end = 12)
```
### Model
#### ARIMA Model
```{r}
arimaModel <- auto.arima(train)
arimaForecast <- forecast(arimaModel, h = 2)
arimaForecast
```
### Visualizations
#### History and Predictions
```{r}
plot(arimaForecast, main = "PageValues", ylab = "PageValues", xlab = "Months")
lines(test, col="red")
legend("topright", lty = 1, bty = "n", col = c("red","blue"), c("Actual","Predicted"))
```
### Only the predictions
```{r}
arimaMean <-arimaForecast$mean

plot(test, main = "PageValues", ylab = "PageValues", xlab = "Months", col = "darkblue")  
lines(arimaMean, col="red")
legend("topleft", lty = 1,bty = "n", col = c("red","blue"), c("Predicted","Actual"))
```

### Summary
***
Time Series analysis is for this dataset not the best choice, because the time period is too short. 
The result of this analysis can be taken as an incentive to improve data quality by collecting data over a longer period of 
time.

***
